\NAME: A framework for \\ Efficient Intrusion Detection\\ in the Internet of Things

### 2014-10-21 paper.tex
added foo-lang syntax highlighting

Listing \ref{lst:watchdog} illustrates some of the features mentioned above,
using a small but representative example of an algorithm: a
watchdog\cite{mishra2004intrusion}. Using a heartbeat, nodes can broadcast a
message at a regular interval, allowing other nodes to monitor its
availability. Missing heartbeats could indicate problems, such as physical
capturing of a certain node.

\lstinputlisting[
  float,
  basicstyle=\small\ttfamily,
  label=lst:watchdog,
  caption=Heartbeat in \NAME
]{src/watchdog.foo}

>>>>

Listing \ref{lst:watchdog} illustrates some of the features mentioned above,
using a small but representative example of an algorithm: a
watchdog\cite{mishra2004intrusion}. Using a heartbeat, nodes can broadcast a
message at a regular interval, allowing other nodes to monitor its
availability. Missing heartbeats could indicate problems, such as physical
capturing of a certain node.
\lstdefinelanguage{foo-lang}{
  emph={module,const,from,import,extend,with,after,do,function,@every,having},
  emphstyle={\textbf},
  morecomment=[l]{//},
  moredelim=[is][]{@@}{@@},       % temp solution to allow keywords without emph
  moredelim=[is][\emph]{!!}{!!}   % temp solution to hightlight #atoms
}

\lstinputlisting[
  language=foo-lang,
  float,
  basicstyle=\footnotesize\ttfamily\color{black},
  label=lst:watchdog,
  caption=Watchdog in \NAME
]{src/watchdog.foo}
